%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% begin Acknowledgements

% Acknowledgements {{{
\begin{acknowledgements}

I would first like to thank my dissertation advisor, Professor Harry H.
Cheng for his continued support during my long, somewhat unorthodox journey
as a student. I would also like to thank the other members of my thesis committee,
as well as the numerous professors and advisors who have guided me on my 
journey.

I would like to thank all of my past and present colleagues at the Integration
Engineering Laboratory for their continued support. I would especially like
to thank Stephen Nestinger and Yu-Cheng Chou for their guidance and example, 
Graham Ryland for being a partner designing new modular robots, Kevin Gucwa and
Binsen Qian for assisting me in the lab, as well as a host of undergraduate students.

I would like to express my deepest gratitude to my parents, family, friends,
and especially my wife, Emily. This document would not exist without the 
support, faith, and love shown to me during my time as a student.

\begin{comment}
I am deeply indebted to my dissertation advisor, Professor Harry H. Cheng for his 
  continued support, encouragement, and invaluable supervision during my 
  graduate studies for the doctorate degree.
I would also like to thank the other members of my thesis committee, Professor 
  Bahram Ravani and Professor Sanjay Joshi for their support and advice during 
  the course of this research project. 
They have been very helpful in discussing design issues related to the project.

I would like to thank all of my colleagues at the Integration Engineering 
   Laboratory for their companionship and continued support during difficult
   times.
In particular, I would like to thank Yu-Cheng Chou for his motivational 
  diligence and hard work, Graham Ryland and David Ko for times spent working 
  on and discussing robotics, and Bo Chen for her strength and dedication which
  helped make this research possible.

I would like to thank the Sandia National Laboratories for providing me with
  the Sandia National Laboratory/UC Davis Excellence in Engineering Graduate 
  Fellowship for my Ph.D. studies.

I would like to express my sincerest appreciation to my parents for their 
  continued support and encouragement, without whom none of this would have
  been possible.
A big thanks to my other family members and all of my close friends for 
  believing in me, supporting me, and encouraging me to do my best. 
\end{comment}

\end{acknowledgements}

% }}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
